### 2015-08-15 fundamentals/conclusion.tex
cleans up reference to physics in conclusion to make note of where physics modules exist. Toward a solution to #128

Similarly the fidelity-agnostic modular architecture facilitates simulations
at every level of detail. Simulations relying on arbitrarily complex isotopic
compositions are possible in \Cyclus, as are simulations not employing any
physics at all. Indeed, agents of such varying fidelity can even exist in the
same simulation. Researchers no longer need to reinvent the wheel in order to
model a simulation focused on the aspects of the fuel cycle
relevant to their research.

>>>>

Similarly, the fidelity-agnostic, modular \Cyclus architecture facilitates simulations
at every level of detail. Simulations relying on arbitrarily complex isotopic
compositions are possible in \Cyclus, as are simulations not employing any
physics at all. To support this, the \Cycamore library provides models 
employing basic physics for core fuel cycle facilities and extension libraries 
from the community more support detailed simulations. Indeed, agents of such 
varying fidelity can even exist in the same simulation. Researchers no longer 
need to reinvent the underlying simulator framework in order to model a simulation 
focused on the aspects of the fuel cycle relevant to their research.
